---
title: "Package Function Explanations"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{What the package does}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753Falast2025)
```

# Introduction
## mymlnorm()

mymlnorm() computes and visualizes the likelihood surface for a normal distribution by evaluating the log-likelihood function over a grid of possible values for the population mean (mu) and standard deviation (sig)

```{r}
set.seed(123)
x <- rnorm(100, mean = 10, sd = 2)
mymlnorm(x, mu = seq(8, 12, length = 100), sig = seq(1, 4, length = 100))
```

## myboot2()

myboot2() performs nonparametric bootstrapping to estimate the sampling distribution of the mean
```{r}
set.seed(123)
x <- rnorm(50, mean = 12, sd = 3)
myboot2(x, iter = 1000)
```

## myclt()

myclt() visually demonstrates the Central Limit Theorem (CLT) by simulating sample means from a normally or uniformly distributed population

```{r}
myclt(n = 30, iter = 10)
```

## myncurve()

myncurve() plots the probability density function (PDF) of a normal distribution and shades the area under the curve to the right of a specified value a

```{r}
myncurve(a = 120, mu=10, sigma=10)
```

## mysq()

mysq() calculates and visualizes the sum of squares for a given numeric vector
```{r}
x <- c(5, 7, 8, 6, 9)
mysq(x)
```

## ntickets()

tickets() calculates the number of airline tickets that should be sold when a plane has a fixed number of seats, and there’s a known probability that a passenger shows up

```{r}
ntickets(N = 100, gamma = 0.05, p = 0.92)
```

## myf()

myf() evaluates a piecewise quadratic function where the quadratic term is applied only when x > 18. It’s used for modeling scenarios where the relationship changes past a threshold

```{r}
myf(20, c(2, 3, 4))     
myf(c(15, 18, 20), c(2, 3, 4))  
```

## mybin()

mybin() simulates a binomial experiment by repeatedly sampling outcomes of success/failure trials and plotting the resulting distribution of successes.

```{r}
mybin(1000, 10, 0.7)
```

